The Optimal Power Flow (OPF) problem is a central tool for the planning and operation of Electric Power Systems (EPS). In the Brazilian context, established industry-grade tools such as CEPEL's ANAREDE incorporate specific control actions (generator reactive power limits (QLIM), bus voltage magnitude limits (VLIM), automatic switched-shunt susceptance control (CSCA), automatic on-load transformer tap control (CTAP) and, under emergency conditions, hierarchical load-shedding/relief schemes, labelled here as DERA after the corresponding script name) that are not natively available in the classical academic formulations implemented by mainstream open-source packages. This work presents the construction, in the Julia language, of an incremental progression of six AC power flow formulations: two reference formulations based on the \textit{PowerModels.jl} package (a full OPF and a classical power flow) and four hand-built \textit{JuMP} formulations in which each of the ANAREDE control actions is sequentially introduced on top of the previous one. Inputs are read from PWF files using the \textit{PWF.jl} package, with extraction of the control structures (DOPC and DLIN) enabled. The non-linear model is solved with the Ipopt solver and the controls are introduced via penalized slack variables in a soft-constraint objective. The six formulations are submitted to a standardized test battery of twenty-seven cases, comprising pedagogical networks of three to nine buses, medium-scale networks (300 and 500 buses), reduced cutouts of the Brazilian Northeast subsystem (\texttt{caso\_red} and \texttt{caso\_red2}) and a snapshot of the Brazilian Interconnected Power System (\texttt{CASO\_VER\_MAXDIU.PWF} from the ONS PAR/PEL 2027-2031 cycle, Summer 2027/2028 Maximum Daily Demand, with 13\,338 buses). Results show that the hand-built formulations converge on a strictly larger set of cases than the \textit{PowerModels} references. In particular, they recover feasible solutions on QLIM-active cases where the classical OPF declares the problem infeasible, and the solutions produced by the CSCA- and CTAP-augmented formulations cluster in numerically distinct groups from the reference, reproducing the expected behavior of ANAREDE's control heuristics.

% Separe as Keywords por ponto
\keywords{Optimal power flow. Electric power systems. JuMP. PowerModels.jl. Control actions. Ipopt.}
